Type Refinements for the Working Class

### 2015-12-22 paper.tex
correct a typo
adjust section heading name
explain our purpose---meaning explanation, not just model

\section{Generalized Predicative Mathematical Foundations}

@@

@@

Then, we say that $\phi$ \emph{globally refines} $\tau$ (written
$\GloballyRefines{\phi}{\tau}$) when we have $\Refines{\cdot}{\phi}{\tau}$.
Furthermore, when $\Refines{\Upsilon}{\phi}{\tau}$, for any renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}
we can clearly define a new refinement $\Refines{\Upsilon'}{\Rename{\rho}{\rho}}{\tau}$.

>>>>

\section{Generalized Predicative Foundations}

@@

Our purpose in fixing a semantic universe is emphatically \emph{not} to give a
mathematical interpretation or model of type theory inside set theory, though
it is possible to read our construction in this metamathematical light---however,
the vocabulary of the pretopos $\SemU$ gives us a perspicuous language in which
to propound what we consider to be an informal (pre-mathematical) meaning
explanation in the sense of Heyting~\cite{heyting:1956} and
Martin-L\"of~\cite{martin-lof:1979}.
\footnote{
  Both Gambino~\cite{gambino:2002} and Dybjer~\cite{dybjer:2012} give lucid
  explanations of the distinction between \emph{meaning theory} and \emph{model theory}.
}

@@

Then, we say that $\phi$ \emph{globally refines} $\tau$ (written
$\GloballyRefines{\phi}{\tau}$) when we have $\Refines{\cdot}{\phi}{\tau}$.
Furthermore, when $\Refines{\Upsilon}{\phi}{\tau}$, for any renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}
we can clearly define a new refinement $\Refines{\Upsilon'}{\Rename{\rho}{\phi}}{\tau}$.
